### 2021-02-18 evaluation.tex
Results: Add results of `vampire -lcm standard`
Improve Evaluation

The raw input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
Each problem is first preprocessed by Vampire:
\gls{fof} problems are converted into equisatisfiable \gls{cnf} problems,
and basic simplifications are performed.
\todo{FB: Explain in more detail or better terms.}
New symbols may be introduced into the problems during preprocessing.
We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.

@@

@@

\texttt{vampire -lcm standard} & ? & ? & ? & ? \\

>>>>

The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by Vampire.
New symbols may be introduced during preprocessing,
namely due to the Tseitin transformation and Skolemization.
We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.

@@

\texttt{vampire -lcm standard} &
\num{3823.0} &
\num[round-mode=places,round-precision=2]{3.40587727318528} &
%\SI[round-mode=places,round-precision=2]{49.9869247}{\percent} &
+53.4 &
\num[round-mode=places,round-precision=3]{1.014165959} \\
% VML-741

@@
